### 2020-08-20 docs/build/assets/SignalFlow/signalflow.tex

\def\mw{1.25cm}
\def\mh{1cm}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=\mw, minimum height=\mh, thick, align=center, ultra thick
    },
    Component/.pic = {
        \node [border](-edge){#1}; 
    },
}

@@

        % Draw connections 
        \begin{scope}[line width=1.5mm, >={Triangle[width=4mm,length=3mm]}]
            \def\shiftamount{0.5mm};
            \draw[->] (gen-edge.east) -- (adder-edge.west);
            \draw[->] (adder-edge.east) -- (gain-edge.west);
            \draw[->] (gain-edge.east) -- (writer-edge.west);
            \draw[->] (gain-edge.east) -- (writer-edge.west);
            \draw[-] (gain-edge.east) -| ++ (0.3cm, -1.5cm) coordinate (a);
            \draw[->] ([yshift=0.75mm] a) -| (adder-edge.south);
        \end{scope}

        % \Place clock 
        \begin{scope}[shift={(-4cm, -2cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] (-4.5, -3) rectangle (4.5, 1);
        \draw (0,0) node[yshift=-2.5cm, xshift=3.5cm]{Model};
    \end{tikzpicture}
\end{document}

>>>>

\def\mw{0.01cm}
\def\mh{0.01cm}

@@

\tikzset{
    border/.style = { 
        draw, circle, inner sep=0pt, align=center, thick
    },
    Component/.pic = {
        \node [border, label={[shift={(0.1pt,0.3pt)}]#1}](-edge){}; 
    },
}

@@

        % Draw connections 
        \begin{scope}[line width=0.25mm, >={Triangle[width=1.25mm,length=1.25mm]}]
            \def\shiftamount{0.5mm};
            \draw[->] (gen-edge.east) -- (adder-edge.west);
            \draw[->] (adder-edge.east) -- (gain-edge.west);
            \draw[->] (gain-edge.east) -- (writer-edge.west);
            \draw[->] (gain-edge.east) -- (writer-edge.west);
            \draw[->] (gain-edge.south) to [out=225,in=315] (adder-edge.south);
        \end{scope}

    \end{tikzpicture}
\end{document}
